A Comparision of Bootstrap Confidence Interval Methods

### 2022-12-06 project/PaperTemplate/paper.Rmd
Added new simulation

```{r run simulation log normal, include = FALSE}

@@

```{r run simulation beta, include = FALSE}
run_simulation_beta <- function(simulation_rep){
  trueparameter <- 0.8

@@

```{r collect data gamma}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10

  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_gamma, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- colSums(df)/sim_reps

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes+10
  }

@@

```{r collect data log normal, include = FALSE}
collect_data_log_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10

  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_log_normal, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes+10
  }

@@

```{r collect data normal}
collect_data_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10

  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_normal, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes+10
  }

@@

```{r collect data beta, include = FALSE}
collect_data_beta <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10

  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_beta, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes+10
  }

@@

```{r, cache = TRUE, eval = FALSE}
set.seed(495)
sim_reps <- 10000

gamma_data <- collect_data_gamma(sim_reps)
write.csv(gamma_data1,"gamma_data1.csv", row.names = FALSE)

normal_data <- collect_data_normal(sim_reps)
write.csv(normal_data1,"normal_data1.csv", row.names = FALSE)
```

```{r, include = FALSE, eval = FALSE}
#beta_data11 <- collect_data_beta(sim_reps)
#write.csv(beta_data1,"beta_data1_100002.csv", row.names = FALSE)

log_normal_data <- collect_data_log_normal(sim_reps)
write.csv(log_normal_data1,"log_normal_data1.csv", row.names = FALSE)

@@

gamma_df <- read.csv(file = 'gamma_data1_10000.csv')
normal_df <- read.csv(file = 'normal_data1_10000.csv')

gamma_df_long <- gamma_df %>%
  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

@@

>>>>

```{r run simulation log normal}

@@

```{r run simulation beta}
run_simulation_beta <- function(simulation_rep){
  trueparameter <- 0.8

@@

```{r collect data gamma}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 7, ncol = 6)
  sample_sizes = 4

  for (i in 1:7) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_gamma, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- colSums(df)/sim_reps

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes*2
  }

@@

```{r collect data log normal}
collect_data_log_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 7, ncol = 6)
  sample_sizes = 4

  for (i in 1:7) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_log_normal, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes*2
  }

@@

```{r collect data normal}
collect_data_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 7, ncol = 6)
  sample_sizes = 4

  for (i in 1:7) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_normal, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes*2
  }

@@

```{r collect data beta}
collect_data_beta <- function(sim_reps) {
  data2 <- matrix(nrow = 7, ncol = 6)
  sample_sizes = 4

  for (i in 1:7) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_beta, 
                        mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes*2
  }

@@

```{r, cache = TRUE}
set.seed(495)
sim_reps <- 10000

gamma_data_4_128 <- collect_data_gamma(sim_reps)
write.csv(gamma_data_4_128,"gamma_data_4_128.csv", row.names = FALSE)

normal_data_4_128 <- collect_data_normal(sim_reps)
write.csv(normal_data_4_128,"normal_data_4_128.csv", row.names = FALSE)

log_normal_data_4_128 <- collect_data_log_normal(sim_reps)
write.csv(log_normal_data_4_128,"log_normal_data_4_128.csv", row.names = FALSE)

beta_data_4_128 <- collect_data_beta(sim_reps)
write.csv(beta_data_4_128,"beta_data_4_128.csv", row.names = FALSE)
```

```{r, include = FALSE, eval = FALSE}

@@

gamma_df <- read.csv(file = 'gamma_data1_10000.csv')
normal_df <- read.csv(file = 'normal_data1_10000.csv')
log_normal_df <- read.csv(file = 'log_normal1_data_10000.csv')

gamma_df_long <- log_normal_df %>%
  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

@@

```{r}
library(boot)

mean.fun <- function(d, i) {
  d <- X[i]
  return (c(mean(d), sd(d)))
}

sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
num_sample_sizes <- length(sample_sizes)
master <- matrix(nrow = num_sample_sizes, ncol = 6)

for(i in 1:num_sample_sizes) {

  sim_reps <- 10000
  norm_contains <- rep(0, sim_reps)
  basic_contains <- rep(0, sim_reps)
  student_contains <- rep(0, sim_reps)
  percentile_contains <- rep(0, sim_reps)
  bca_contains <- rep(0, sim_reps)

  boot_reps <- 2000
  n <- sample_sizes[i]
  true_mean <- exp(1/2)

  set.seed(495)
  for (j in 1:sim_reps) {
    X <- rlnorm(n, 0, 1)
    values <- data.frame(X)

    results <- boot(data = values, statistic = mean.fun, R = boot_reps)
    results
    #plot(results)
    ci <- boot.ci(results, type = "all")

    norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
    basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
    student_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
    percentile_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
    bca_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]

  }

  master[i, 1] <- sample_sizes[i]
  master[i, 2] <- sum(norm_contains)/sim_reps
  master[i, 3] <- sum(basic_contains)/sim_reps
  master[i, 4] <- sum(student_contains)/sim_reps
  master[i, 5] <- sum(percentile_contains)/sim_reps
  master[i, 6] <- sum(bca_contains)/sim_reps

}
